Appendix

### 2020-04-21 appendix/appendixV5.Rmd
ggplot2-esque forestplot

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: pdf_document 
---

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)

f1 <- grid.grab()

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3,
       test.subgroup.random = TRUE)

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
f2 <- grid.grab()

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f3 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f4 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f5 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f6 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f7 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
f8 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system"}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3,
       test.subgroup.random = TRUE)
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE)
f9 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f10 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f11 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f12 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f13 <- grid.grab()
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)"}
forest(mod, sortvar = -TE, layout = "RevMan5", comb.fixed = FALSE,
       prediction = TRUE, digits.se = 3)
f14 <- grid.grab()
```

@@

>>>>

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
output: pdf_document
---

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f1 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f1
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)

mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f1b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f1b
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f2 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f2

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f3 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f3
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f4 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f4
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f5 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f5
```

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f6 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f6
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f7 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f7
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of lower houses size (N) on Per Capita Expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f8 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f8

@@

```{r, echo=FALSE, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f8b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f8b
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on percentage of public expenditure GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B"))

f9 <- mod2 %>%
  ggplot(aes(y = reorder(studlab,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank()) 
f9
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=3, fig.cap="Effect of lower houses size (N) on log of per capita expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f10 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f10
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the GDP share of public expenditure (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f11 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f11
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of log lower houses size (logN) on the log of per capita government expenditure (logExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f12 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f12
```

@@

```{r, echo=FALSE, fig.width=7, fig.height=4, fig.cap="Effect of upper house size (K) on the per capita government expenditure (ExpPC)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f13 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f13
```

@@

```{r, echo=FALSE, fig.width=8, fig.height=4, fig.cap="Effect of upper house size (K) on the public expenditure share of the GDP (PCTGDP)",warning=FALSE}
mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f14 <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(color = "black") +
  # Error Bars
  geom_errorbarh(height = 0.1) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels= function(x) str_replace(x, "_[0-9]*$", "")) + 
  # Vertical dashed line
  geom_vline(xintercept=0, color="black", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") + 
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") + 
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank())

f14
```

@@

\newpage
```{r, echo=FALSE, fig.width=17, fig.height=24}

#grid.arrange(f8, f9, f11, 
#             f10,f12, f13,
#             f14,
#             ncol = 2,
#             nrow = 4)
#library(ggplot2)

print(ggpubr::ggarrange(f8, f9, f11, 
             f10,f12, f13,
             f14,
          ncol = 2,
          nrow = 4)) + rotate()

#ggpubr::ggarrange(f8) + rotate()
#ggpubr::ggarrange(f9) + rotate()
